Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-30 manuscript/paper-tycho.tex
Kepler constants, simple fits; updated abstract
Simple model fits to Kepler FWHMs, test Cas A FWHMs.
Confirm Tycho radio spectral index.  Add revised paper (AAS) abstract,
meeting notes.

\begin{abstract}
Many young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims are strong evidence for strong
magnetic field amplification, requiring shock-accelerated electrons to radiate
and cool rapidly downstream of the shock.  But, magnetic field damping
immediately behind the shock could produce similarly thin rims.  Synchrotron
loss-limited rim widths should decrease with energy whereas damping limited
rims should be relatively energy-independent.  To discriminate between models,
we measured rim widths around Tycho's supernova remnant in 5 energy bands using
an archival $750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing
energy, favoring loss-limited radiation over magnetic damping and corroborating
similar observations in the remnant of SN 1006 (Ressler et al., 2014).
Observed widths are best fit by electron transport models requiring amplified
magnetic fields of $\abt200$--$1000 \unit{\mu G}$ and particle diffusion
coefficients $\abt 1$--$100\times$ Bohm values, consistent with prior work
on Tycho's SNR.  Non-negligible diffusion results in some degeneracy between
magnetic field strength and diffusion coefficient in setting observed rim
widths, but strong magnetic fields are required for all measurements.  A
different approach may be needed to better constrain diffusion at supernova
remnant shocks.
\end{abstract}

@@

% TODO GENERAL WARNING -- DATA ARE NOT ALL FULLY CONSISTENT AT THIS TIME.
% (spectra/profiles/fwhms/fits).  Will be corrected / good to go in final
% revision.

@@

>>>>

\begin{abstract}
\note[Aaron]{Clone of AAS abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  Synchrotron loss-limited
rim widths should decrease with energy whereas damping limited rims should be
relatively energy-independent.  To discriminate between models, we measured rim
widths around Tycho's supernova remnant in 5 energy bands using an archival
$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
favoring loss-limited radiation over magnetic damping and corroborating similar
observations in the remnant of SN 1006. Observed widths are best fit by
electron transport models requiring amplified magnetic fields of
$\abt200$--$1000 \unit{\mu G}$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
Non-negligible diffusion results in some degeneracy between magnetic field
strength and diffusion coefficient in setting observed rim widths, but strong
magnetic fields are required for all measurements.  A different approach may be
needed to better constrain diffusion at supernova remnant shocks.
\end{abstract}

@@

% TODO GENERAL WARNING -- DATA ARE NOT ALL FULLY CONSISTENT AT THIS TIME.
% (spectra/profiles/fwhms/fits).

@@

Brief (possibly obvious) remark: these estimates of magnetic fields should be
lower bounds, if we neglect diffusion (and compression ratio/etc...).
A spherical projection is the narrowest filament we can get.
Any rippling effects, etc... hmm.  Rippling could strengthen the filament,
making it look at little thinner actually.  But we don't know how big an effect
that could be.  And we are looking at a tangential slice.  There is some room
for ripples/waveforms to accumulate, of course... we see them elsewhere, we do
see distinct filaments stacking.

(maybe something useful / fun to do: what's the projection factor for a rippled
sphere?  Estimating some wavelength from observed stripes, ripple
lengthscale from width of filaments viewed face on (e.g. in Kepler).  Likely,
not gonna make much difference.  But could be helpful to have an idea of how
good/bad this assumption of a spherical shell is, and how much effect that has
on our magnetic field estimates)
